Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-28 appendix.tex

\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
\end{figure}
\end{appendix}

>>>>

\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
\end{figure}
\end{appendix}

### 2020-05-28 manuscript.tex

\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-Phoenix}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-icews}
\end{figure}
\end{appendix}

>>>>

\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-Phoenix}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-Phoenix}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-Phoenix}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-Phoenix}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-Phoenix}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-Phoenix}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-Phoenix}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-Phoenix}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-Phoenix}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-Phoenix}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-Phoenix}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-Phoenix}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-icews}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-icews}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-icews}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-icews}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-icews}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-icews}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-icews}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-icews}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-icews}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-icews}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-icews}
\end{figure}
\begin{figure}[H]
\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-icews}
\end{figure}
\end{appendix}
